# Week 2 Project

## Nicola Morrow

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

I will be using data from the Macalester College library. The data is copied from http://tiny.cc/dcf/Library-small.rda.

##**Basics**

```{r}
load("Library-small.rda")
```

Number of cases in Inv:
```{r}
nrow(Inv)
```

Names of variables in Inv:
```{r}
names(Inv)
```

Number of cases in Bks:
```{r}
nrow(Bks)
```

Names of variables in Bks:
```{r}
names(Bks)
```

Number of books with each different Current.status:
```{r}
Inv %>%
  group_by(Current.Status) %>%
  tally()
```

How many books have been checked out? 
```{r}
X <- Inv %>%
  group_by(Issued.Count) %>%
  tally()
```

This table has two colums. The first shows the number of times a book has been issued. The second column shows how many books have been issued that many times. For example, there are 996 books that have been issued 0 times. There are 337 books that have been issued once. And so on. 