# Week 4 Short Answer Questions

## Nicola Morrow

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

### 8.1 

a) 2 

b) 2

c) 1

d) 5

e) 3

f) 4

g) 4

h) 5

i) 4

### 8.2 

1. 

CPS85 %>% 
  ggplot(aes(x= age, y=wage, shape=married))
  + facet_wrap(~sector)

2. 

CPS85 %>% 
  ggplot(aes(x= age, y=wage))
  + facet_grid(~sector, married)

### 8.3 

Frame <-
  CPS85 %>%
  ggplot(aes(x=age, y=wage))
  
Graph A. 

Frame + geom_point()

Graph B. 

Frame + geom_point(aes(shape=sex))

Graph C. 

Frame + geom_point(aes(shape=sex)) + facet_grid(married)

Graph D. 

Frame + geom_point(aes(shape=married)) + ylim(0,30)

### 9.1 

a. quick presentation 

b. data verb

c. transformation 

d. summary function 

e. data verb

f. quick presentation

g. data verb

h. data verb

i. quick presentation 

### 9.3 

1. 
```{r}
data(diamonds)

diamonds %>%
  group_by(color) %>%
  summarise(size=mean(carat, na.rm = TRUE)) %>%
  arrange(desc(size)) %>%
  head(5)

diamonds %>%
  group_by(clarity) %>%
  summarise(avetable=mean(table, na.rm = TRUE)) %>%
  arrange(desc(avetable)) %>%
  head(5)
```
