# Week 6 Short Answer Questions

## Nicola Morrow 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

### 12.1 

```{r}
BabyNames %>% 
  group_by(sex,name) %>%
  summarise(count = sum(count)) %>%
  mutate(popularity =rank(desc(count))) %>%
  filter(popularity <= 5)
```

### 12.2 

```{r}
PopularCounts <-
  BabyNames %>%
  group_by(year,name) %>%
  summarise(total = sum(count)) %>%
  mutate(ranking = ifelse(rank(desc(total)) <= 100, "Top_100", "Below")) %>%
  group_by(year,ranking) %>%
  summarise(total=sum(total))

GlyphReady <-
  PopularCounts %>%
  spread(ranking, total) %>%
  mutate(frac_in_top_100 = Top_100 / (Top_100 + Below))

GlyphReady %>%
  ggplot(aes(x=year, y=frac_in_top_100)) + geom_line() + ylim(0, NA)
```

### 12.3 

a. summary function 

b. neither summary nor transformation

c. summary function 

d. transformation function 

e. transformation function 

f. summary function 

g. transformation function 

h. summary function 

### 13.1 

1. There are 7 certices: China, France, Germany, Italy, UK, USA, USSR 

2. There is one row for each edge, so 9 edges 

### 13.2 

1. The vertices are A, B, C, and D. 

2. Table 2 shows the edges correctly. 

3. Table 1 shows a connection between B and C, which does not exist. Table 3 shows two edges in one row. 

### 13.3 

NA

### 13.4 

1. Exports is mapped to the size of the letter. 

2. Population is mapped to the shape of the gray symbol 

### 14.1 

```{r}
mosaicData::CPS85 %>%
  ggplot(aes(x=sex, y=wage)) + geom_boxplot(aes(fill=sex))
```

### 14.3

A little less than 1.6 meters for women; around 1.75 meters for men 

### 14.7 

```{r}
mosaicData::CPS85 %>%
  ggplot(aes(x=educ, y=wage, color=sex)) + geom_point() + stat_smooth(method="lm") + ylim(0,15) 
```

### 14.10

```{r}
mosaicData::Galton %>%
  ggplot(aes(x=height, color=sex)) + geom_density() + ylim(0,0.2) + xlim(55,80)
```


