# Week 7 Short Answer Questions

## Nicola Morrow

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

### 15.1 

"April 30th, 1777" = mdy()

"06-23-1912" = mdy()

"3 March 1847" = dmy()

"11:00 am on Nov. 11th, 1918 at 11:00 am" = mdy_hm()

"July 29, 1969" = mdy()

### 15.2 

a. tidyr::extract_numeric()

b. tidyr::extract_numeric()

c. as.numeric

d. tidyr::extract_numeric()

e. as.numeric and tidyr::extract_numeric()

f. as.numeric and tidyr::extract_numeric()

g. as.numeric and tidyr::extract_numeric()

h. tidyr::extract_numeric()

i. tidyr::extract_numeric()

### 16.1 

```{r}
BabyNames %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(total=sum(count)) %>%
  filter(grepl("[aeiou]$", name)) %>%
  arrange(desc(total)) %>%
  head(10)
```

### 16.3 

1. Each matched string will be two letters. 

2. For a pattern like A[LKSZRAP], there are seven strings that match. For a pattern like D[EC], there are two strings that match (DE and DC). For a pattern like RI, there is only one string that matches. There are 61 patterns in total. 

3. These are abbreviations for U.S. states. 

### 16.4 

```{r}
BibleNames <- 
  read.file("http://tiny.cc/dcf/BibleNames.csv")

BibleNames %>%
  filter(grepl("bar", name, ignore.case = TRUE))

BibleNames %>%
  filter(grepl("dam", name, ignore.case = TRUE))

BibleNames %>%
  filter(grepl("lory", name, ignore.case = TRUE))
```

