# Week 3 Project

## Nicola Morrow

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

## Deconstructing graphics

This is a density plot. 

The variables in these graphs include: sex, body mass index, and pregnancy status. 

The sex variable is indicated by color and shows the difference in BMI between males and females. Body mass index is indicated by position along the x axis. Pregnancy status helps show the difference in BMI between pregnant and non-pregnant people, and is indicated by facet. 

There is no data-variable being used for the y-axis in in Figure 2 because it is the second facet of the image, and it is implied that it has the same y-axis as the first facet. 

```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = sex)) + facet_wrap(~ pregnant)
```

## Diamonds

### 1

```{r}
data("diamonds")

diamonds %>% 
  group_by( color ) %>% 
  summarise( average=mean(carat) ) %>% 
  arrange(desc( average )) %>% 
  head( 10 )
```

Diamonds of the color "J" (worst) seem to be the largest. 

### 2
```{r}
diamonds %>% 
  group_by( clarity ) %>% 
  summarise( average=mean(table) ) %>% 
  arrange(desc( average )) %>% 
  head( 10 )
```

Diamonds of the clarity "I1" (worst) seem to have the largest average table. 

## Voting

### 1 

```{r}
data(Minneapolis2013)

tally(Minneapolis2013)
```

There are 80,101 cases. 

### 2 

```{r}
Minneapolis2013 %>% 
  group_by(Second) %>%
  tally() %>%
  arrange(desc(n)) %>%
  head(5)
```

### 3 

```{r}
Minneapolis2013 %>% 
  filter(First=="undervote") %>%
  tally()
```

There were 834 ballots marked "undervote" in First choice selections. 

```{r}
Minneapolis2013 %>% 
  filter(Second=="undervote") %>%
  tally()
```

There were 10,598 ballots marked "undervote" in Second choice selections. 

```{r}
Minneapolis2013 %>% 
  filter(Third=="undervote") %>%
  tally()
```
 
There were 19,210 ballots marked "udnervote"in Third choice selections. 

### 4 

```{r}
Minneapolis2013 %>% 
  filter(First=="BETSY HODGES") %>%
  group_by(Second) %>%
  summarise(topSecond=n()) %>%
  arrange(desc(topSecond)) %>%
  head(3)
```

### 5 

```{r}
Minneapolis2013 %>% 
  group_by(Precinct) %>%
  summarise(fraction=mean(First=="undervote")) %>%
  arrange(desc(fraction)) %>%
    head(1)
```
